---

title: "SE project Edmonds Data exploration and question"
author: "Darius McDaniel"
date: "November 20, 2015"
output: html_document
---

----------

## This document will aim to answer different questions from the edmonds data. There will be a question answered for most of the main topics covered in this semesters class.

All programs will be added and committed to github and found here : https://github.com/djmcdan/SE_Project.git


```{r, include=FALSE}

#SE_projectPackages

library(data.table)
library(bit64)
library(plyr)
library(dplyr)
library(DescTools)
library(lubridate)
library(ggplot2)
library(googleVis)
library(lattice)
library(ggmap)
library(zipcode)
library(RJSONIO)
library(RCurl)
library(dplyr)


```

```{r, include=FALSE}
setwd("C:/Users/Darius/Documents/DF2015_Data/DF2015_revised") 

#SE_projectData
visitor <- fread("visitor.csv",stringsAsFactors=FALSE)
transactions <- fread("transactions.csv",stringsAsFactors=FALSE)
shopping <- fread("shopping.csv",stringsAsFactors=FALSE)
leads <- fread("leads.csv",stringsAsFactors=FALSE)
configuration <- fread("configuration.csv",stringsAsFactors=FALSE)


```

Now we start with questions for exploration in 5 topics discussed this semester around using Dyplyr, Visualizations, sqldf, objects and JSON/XML to answer different questions with the Edmonds car data. 

Questions

    1. Dplyr. 
        
    Based on the visitor data how long did the visits last and did the longer visit times lead to purchases or vis versa?
    
       

To first answer this question we must do some data cleaning. 

```{r, include=FALSE}



#Question a.
visitor_time <- visitor %>% 
  mutate(new_dwell_time_mins = new_dwell_time/60, used_dwell_time_mins = used_dwell_time/60 , tot_dwell_time_mins =   tot_dwell_time/60 , tot_dwell_time_hours = tot_dwell_time_mins/60)%>% 
  select(visitor_key, tot_dwell_time, tot_dwell_time_mins,tot_dwell_time_hours, zip)


sum_visitor_time <- visitor_time %>% group_by(visitor_key)%>% summarise(hours_sum_time = sum(tot_dwell_time_hours, na.rm = TRUE))


mean_med_visitor_time <-sum_visitor_time %>% summarise(mean_hours_visited = mean(hours_sum_time , na.rm = TRUE),median_hours_visited = median(hours_sum_time , na.rm = TRUE))

#Question b.



new_bought <- transactions  %>% filter(new_or_used_bought == "N") %>% select(visitor_key, date_sold, new_or_used_bought, price_bought,model_bought,make_bought,model_year_bought,mileage_bought,bodytype_bought,zip_bought)%>% distinct()
used_bought <- transactions %>% filter(new_or_used_bought == "U") %>% select(visitor_key, date_sold, new_or_used_bought, price_bought,model_bought,make_bought,model_year_bought,mileage_bought,bodytype_bought,zip_bought)%>% distinct()



visitor_purchased_new <- sum_visitor_time %>%inner_join(new_bought)%>% distinct()
visitor_purchased_used <- sum_visitor_time %>%inner_join(used_bought)%>% distinct()

avgs_visitor_time_purchaseNw <-visitor_purchased_new %>% summarise(min_hours_visited = min(hours_sum_time , na.rm = TRUE), mean_hours_visited = mean(hours_sum_time , na.rm = TRUE),med_hours_visited = median(hours_sum_time , na.rm = TRUE), max_hours_visited = max(hours_sum_time , na.rm = TRUE))
avgs_visitor_time_purchaseUs <-visitor_purchased_used %>% summarise(min_hours_visited = min(hours_sum_time , na.rm = TRUE), mean_hours_visited = mean(hours_sum_time , na.rm = TRUE),med_hours_visited = median(hours_sum_time , na.rm = TRUE), max_hours_visited = max(hours_sum_time , na.rm = TRUE))



#Question c.

new_bought_cat <- visitor_purchased_new %>% mutate(time_hours_cat = ifelse(hours_sum_time < 1, 1, ifelse(hours_sum_time >= 1 & hours_sum_time < 5,2,
                                                                                                               ifelse(hours_sum_time >= 5 & hours_sum_time < 10,3,   
                                                                                                                      ifelse(hours_sum_time >= 10 & hours_sum_time < 20,4,
                                                                                                                             ifelse(hours_sum_time >= 20 & hours_sum_time < 48,5,
                                                                                                                                    ifelse(hours_sum_time >= 48 & hours_sum_time < 72,6,
                                                                                                                                           ifelse(hours_sum_time >72,7,NA)))))))) 
new_bought_cat$time_hours_cat<- factor(new_bought_cat$time_hours_cat, levels = c(1,2,3,4,5,6,7), labels = c(">1hr", " 1-5hrs", " 5-10hrs","10-20hrs","20-48hrs", "48-72hrs", ">72hrs")) 



used_bought_cat <- visitor_purchased_used %>% mutate(time_hours_cat = ifelse(hours_sum_time < 1, 1, ifelse(hours_sum_time >= 1 & hours_sum_time < 5,2,
                                                                                                                 ifelse(hours_sum_time >= 5 & hours_sum_time < 10,3,   
                                                                                                                        ifelse(hours_sum_time >= 10 & hours_sum_time < 20,4,
                                                                                                                               ifelse(hours_sum_time >= 20 & hours_sum_time < 48,5,
                                                                                                                                      ifelse(hours_sum_time >= 48 & hours_sum_time < 72,6,
                                                                                                                                             ifelse(hours_sum_time >72,7,NA)))))))) 


used_bought_cat$time_hours_cat<- factor(used_bought_cat$time_hours_cat, levels = c(1,2,3,4,5,6,7), labels = c(">1hr", " 1-5hrs", " 5-10hrs","10-20hrs","20-48hrs", "48-72hrs", ">72hrs")) 

#Question d.


milage_bought_new <- new_bought_cat %>% mutate(mileage_cat100 <-ifelse(mileage_bought <= 100, 1, ifelse(mileage_bought > 100,2,0))) 

milage_bought_new$year_purchased <- as.numeric( format( as.Date( milage_bought_new$date_sold, origin='1900-1-1'), '%Y'))

milage_bought_used <- used_bought_cat %>% mutate(mileage_cat100 <-ifelse(mileage_bought <= 100, 1, ifelse(mileage_bought > 100,2,0))) 

 milage_bought_used$year_purchased <- as.numeric( format( as.Date( milage_bought_used$date_sold, origin='1900-1-1'), '%Y'))

```

Answers to posed questions

```{r}
#a. What was the average,min and max time spent on the site for all visits
mean_med_visitor_time


#b. Now for those that purchased new or used car what was the avg time visited?

avgs_visitor_time_purchaseNw
avgs_visitor_time_purchaseUs



#c. How many purchases were  >1hr, 1-5, 5-10,10-20, gt20 hrs


table(new_bought_cat$time_hours_cat )
table(used_bought_cat$time_hours_cat )

histogram(new_bought_cat$time_hours_cat)
histogram(used_bought_cat$time_hours_cat)

#Observation Over 50percent of purchases that happened within an hour of visiting the site for new and used cars

#d. How many new cars had less than 100 miles on them and greater than 100 miles?

#New
  table(milage_bought_new$mileage_cat100 )

#Used 
  table(milage_bought_used$mileage_cat100 )




```       
        

    2. Visualizations ( googlevis, ggplot2)
        
       a.Using zip codes provided from transactions data map the purchases using googlevis?
       b.Than look the transactions separated by the year the car was purchased using ggplot2 . 

```{r, include=FALSE}
 
zipcode_tran <- transactions %>% mutate(zip = zip_bought) %>% select(zip) %>% distinct()
data(zipcode)

milage_bought_new <- milage_bought_new %>% mutate(zip = as.factor(zip_bought))
milage_bought_used <- milage_bought_used %>% mutate(zip = as.factor(zip_bought))

  
new_bought_latlon = merge(milage_bought_new,zipcode, by.x='zip', by.y='zip') 
use_bought_latlon = merge(milage_bought_used,zipcode, by.x='zip', by.y='zip') 



#Googlevis

#Paste the lat and long together for googlevis
new_bought_latlon$LatLon <- paste(round(new_bought_latlon$latitude,2),round(new_bought_latlon$longitude,2),sep=":")
use_bought_latlon$LatLon <- paste(round(use_bought_latlon$latitude,2),round(use_bought_latlon$longitude,2),sep=":")

#Remove any NAs in both
new_bought_latlon_ <- new_bought_latlon[new_bought_latlon$LatLon != "NA:NA",] 
use_bought_latlon_ <- use_bought_latlon[use_bought_latlon$LatLon != "NA:NA",]

#Plot
new_bought_latlon_.plot <- gvisMap(new_bought_latlon_, "LatLon" ,
                                   options=list( showLine=TRUE, enableScrollWheel=TRUE,
                                                 mapType='hybrid', useMapTypeControl=TRUE,
                                                 width=1500,height=800))



use_bought_latlon_.plot <- gvisMap(use_bought_latlon_, "LatLon" ,
              options=list( showLine=TRUE, enableScrollWheel=TRUE,
                           mapType='hybrid', useMapTypeControl=TRUE,
                           width=1500,height=800))


plot(new_bought_latlon_.plot)
plot(use_bought_latlon_.plot)


#Now will use ggplot to look by year

statecount_nbll <- new_bought_latlon_ %>% group_by(state,year_purchased) %>% summarise(n = n ()) %>% mutate(ct = n/100)
statecount_ubll <- use_bought_latlon_ %>% group_by(state,year_purchased) %>% summarise(n = n ()) %>% mutate(ct = n/100)



statecount_nbll$region_ <- state.name[match(statecount_nbll$state,state.abb)]
statecount_nbll$region <- tolower(statecount_nbll$region_)

statecount_ubll$region_ <- state.name[match(statecount_ubll$state,state.abb)]
statecount_ubll$region <- tolower(statecount_ubll$region_)

#Map of new cars purchased in the US from 2013-2015

us <- map_data("state")

gg_nw <- ggplot() + geom_map(data=us, map=us,
                    aes(x=long, y=lat, map_id=region),
                    fill="#ffffff", color="#ffffff", size=0.15)
gg_nw <- gg_nw + geom_map(data=statecount_nbll, map=us,
                    aes(fill=n, map_id=region),
                    color="#ffffff", size=0.15) + facet_wrap(~ year_purchased) 
#Want to see them the maps horizontally and in new color

gg_nw <- gg_nw + scale_fill_continuous(low='thistle2', high='darkred', 
                                 guide='colorbar')+ facet_wrap(~ year_purchased, ncol = 1)  + labs(title = "Map of New purchased cars in US")  
gg_nw

#Want to make it look alittle better 
gg_nw <- gg_nw + labs(x=NULL, y=NULL) + coord_map("albers", lat0 = 39, lat1 = 45) + theme(panel.border = element_blank())  + theme(panel.background = element_blank()) + theme(axis.ticks = element_blank()) + theme(axis.text = element_blank())
gg_nw

##Map of used cars purchased in the US from 2013-2015
gg_us <- ggplot() + geom_map(data=us, map=us,
                          aes(x=long, y=lat, map_id=region),
                          fill="#ffffff", color="#ffffff", size=0.15)
gg_us <- gg_us + geom_map(data=statecount_ubll, map=us,
                          aes(fill=n, map_id=region),
                          color="#ffffff", size=0.15) + facet_wrap(~ year_purchased) 

#Want to see them the maps horizontally and in new color

gg_us <- gg_us + scale_fill_continuous(low='thistle2', high='darkred', 
                                       guide='colorbar')+ facet_wrap(~ year_purchased, ncol = 1) + labs(title = "Map of Used purchased cars in US")  

gg_us

#Want to make it look alittle better 

gg_us <- gg_us + labs(x=NULL, y=NULL) + coord_map("albers", lat0 = 39, lat1 = 45) + theme(panel.border = element_blank())  + theme(panel.background = element_blank()) + theme(axis.ticks = element_blank()) + theme(axis.text = element_blank())
gg_us
 
 
 
```


```{r}
#a.
plot(new_bought_latlon_.plot)
plot(use_bought_latlon_.plot)

#b.
gg_nw
gg_us
```
 
 
 c. SQL (sqldf / Rsqlite)
    

      a. Create a SQLite database and figure out : How many new cars where bought by manufactuer year ?, How many different body types were purchased new and used displaying only the top 10 ?,  What are the top five makers that sold the most new and used cars?,
      b.  What are the average, min and max mileages bought along with the average, min and max price bought?


```{r, echo=FALSE, message=F, warning=F}    

library(sqldf)
library(tcltk)
library(RSQLite)

#Create the SQLite data base

setwd("C:/Users/Darius/Documents/DF2015_Data/DF2015_revised") 
  
db <- dbConnect(SQLite(), dbname="Edmonds.sqlite")

setwd("C:/Users/Darius/Documents/DF2015_Data/DF2015_revised") 

#Below write the different dataset into sql tables. Please uncomment if this is your first run to creat the database.

# dbWriteTable(conn = db, name = "Visitor_", value = "visitor.csv",
#              row.names = FALSE, header = TRUE)
# dbWriteTable(conn = db, name = "Transactions_", value = "transactions.csv",
#              row.names = FALSE, header = TRUE)
# dbWriteTable(conn = db, name = "Configuration_", value = "configuration.csv",
#              row.names = FALSE, header = TRUE)
# dbWriteTable(conn = db, name = "Leads_", value = "leads.csv",
#              row.names = FALSE, header = TRUE)
# dbWriteTable(conn = db, name = "Shopping_", value = "shopping.csv",
#              row.names = FALSE, header = TRUE)


# The tables in the database
dbListTables(db)     

# The columns in Visitor and Transactions
#dbListFields(db, "Visitor_")         
#dbListFields(db, "Transactions_")  
```

#Queries for Questions in the database

```{r}
      
#Lets see how many new cars where bought by manufactuer year

dbGetQuery(db,"SELECT model_year_bought as Model_year_purchased_New, count(*) as modelYR_freq from Transactions_  WHERE new_or_used_bought = 'N' GROUP BY model_year_bought")

dbGetQuery(db,"SELECT model_year_bought as Model_year_purchased_Used, count(*) as modelYR_freq from Transactions_  WHERE new_or_used_bought = 'U' GROUP BY model_year_bought")


#How many different body types were purchased new and used displaying only the top 10

dbGetQuery(db,"select bodytype_bought, count(*) as freq from Transactions_ WHERE new_or_used_bought = 'N' group by bodytype_bought order by freq desc LIMIT 10")
dbGetQuery(db,"select bodytype_bought, count(*) as freq from Transactions_ WHERE new_or_used_bought = 'U' group by bodytype_bought order by freq desc LIMIT 10")


#What are the top five makers that sold the most new and used cars 

dbGetQuery(db,"select make_bought, count(*) as freq from Transactions_ WHERE new_or_used_bought = 'N'  GROUP BY make_bought  order by freq desc LIMIT 5")

dbGetQuery(db,"select make_bought, count(*) as freq from Transactions_ WHERE new_or_used_bought = 'U' GROUP BY make_bought order by freq desc LIMIT 5")

#Honda and Toyota both have the most purchases for new and used


#What was the average, min and max mileages bought along with the average, min and max price bought for the top ten

#New
dbGetQuery(db,"select make_bought, count(*) as freq, min(price_bought), avg(price_bought), max(price_bought),min(mileage_bought),  avg(mileage_bought), max(mileage_bought)  
      from Transactions_ WHERE new_or_used_bought = 'N'  GROUP BY make_bought order by freq desc LIMIT 10")
#Used
dbGetQuery(db,"select make_bought, count(*) as freq, min(price_bought), avg(price_bought), max(price_bought),min(mileage_bought),  avg(mileage_bought), max(mileage_bought)  
      from Transactions_ WHERE new_or_used_bought = 'U'  GROUP BY make_bought order by freq desc LIMIT 10")



#Honda and Toyota both have the most purchases for new and used


```        

 #d. Objects
    
    Questions
    
    a.Create printout of the data created to look at purchases of new cars bought with over 100 miles and used cars with under 100 miles.

    b.Summarize the total purchase amounts .
    
    c.Plot using ggmap to see where purchases of new cars bought with over 100 miles and used cars with under 100 miles were.
    
```{r}    



NewMilesOver100 <- transactions %>% filter(mileage_bought >100 & new_or_used_bought == "N")
UsedMilesUnder100 <- transactions %>% filter(mileage_bought < 100 & new_or_used_bought == "U")

#Create Object

cardata <- function(m,x,y,z) {
  Edcars <- list(title = m, id=x, source=y, data=z)
  class(Edcars) <- "cars"
  return(Edcars)
}

PurchasedNewOver100 <- cardata("New Cars Purchased with Miles Over 100 in","US","http://www.edmunds.com",NewMilesOver100)
PurchasedUsedUnder100 <- cardata("Used Cars Purchased with Miles Under 100 in","US","http://www.edmunds.com",UsedMilesUnder100)

#a.

print.cars <- function(object) {
  header <- paste("Data:",object$title,"Country:",object$id,"SOURCE:",object$source,sep=" ")
  cat(header,"\n\n")
  str(object$data,0)
}



#Want to see all all the people who bought cars over or under 100 miles new and used

#b.

plot.cars <- function(object,...) {
   df <- object$data

  
  zipcode_tran <- df %>% mutate(zip = zip_bought) %>% select(zip) %>% distinct()
  library(zipcode)
  data(zipcode)
  
  dfout <- df %>% mutate(zip = as.factor(zip_bought),year_purchased = as.numeric( format( as.Date( date_sold, origin='1900-1-1'), '%Y')))
  
  dfout_latlon = merge(dfout,zipcode, by.x='zip', by.y='zip') 

  
  p <- qmplot(longitude, latitude, data = dfout_latlon, colour = I("red"),size = I(2), darken = .1) + facet_wrap(~ year_purchased, ncol = 1) +  expand_limits() + theme_minimal()

  
  plot(p)
  }

#c.
summary.cars <- function(object) {
 
  df <- object$data
   sum <- df %>% summarise(mean_price_purchased = mean(price_bought , na.rm = TRUE),lowest_price_purchased = min(price_bought , na.rm = TRUE),highest_price_purchased = max(price_bought , na.rm = TRUE) )
     
  print(sum)
}



    
```  

Answers
```{r}
 #a.Create printout of the data created to look at purchases of new cars bought with over 100 miles and used cars with under 100 miles.

    print(PurchasedNewOver100)
    print(PurchasedUsedUnder100)


 #b.Summarize the total purchase amounts .
    
    summary(PurchasedNewOver100)
    summary(PurchasedUsedUnder100)
    
 #c.Plot using ggmap to see where purchases of new cars bought with over 100 miles and used cars with under 100 miles were.
    
    plot(PurchasedNewOver100)
    plot(PurchasedUsedUnder100)

    
    
    
   
```
 
 e.JSON
  
  Create a data frame based on top makes and models bought in each year attach consumer ratings using Edmonds API?
  
```{r}
      
     
     
setwd("C:/Users/Darius/Documents/DF2015_Data/DF2015_revised") 

db <- dbConnect(SQLite(), dbname="Edmonds.sqlite")

#First what are the top 5 makes bought

dbGetQuery(db,"select make_bought, count(*) as freq,model_bought,model_year_bought from Transactions WHERE new_or_used_bought = 'N'  GROUP BY make_bought,model_bought  order by freq desc LIMIT 5")

# Honda has the top four purchased. The new models are 2015 Accord, 2014 CR-V, 2015 Civic and 2015 Odyssey.
# followed by Suburu Forester 2015.


dbGetQuery(db,"select make_bought, count(*) as freq,model_bought,model_year_bought from Transactions WHERE new_or_used_bought = 'U'  GROUP BY make_bought,model_bought  order by freq desc LIMIT 5")

# Honda has the top three used purchased. The use models are 2011 Accord, 2014 CR-V and 2011 Civic.
# followed by 2014 BMW 3 Series and 2011 Toyota Camry.

# Lets save this query plus add 5 more for below and add an id

TopNew_data<- dbGetQuery(db,"select make_bought as make, count(*) as freq,model_bought as model,model_year_bought as year 
                      from Transactions WHERE new_or_used_bought = 'N'  GROUP BY make_bought,model_bought  order by freq desc LIMIT 5") 
TopNew_data<-  mutate(TopNew_data,id = as.character(rownames(TopNew_data),levels=rownames(TopNew_data)))




TopUsed_data<- dbGetQuery(db,"select make_bought as make, count(*) as freq,model_bought as model,model_year_bought as year 
                      from Transactions WHERE new_or_used_bought = 'U'  GROUP BY make_bought,model_bought  order by freq desc LIMIT 5") 
TopUsed_data<- TopUsed_data %>%  mutate(id = as.character(rownames(TopUsed_data),levels=rownames(TopUsed_data)), model = gsub(" ", "-", model, fixed = TRUE)) 
TopUsed_data$model <-gsub(" ", "-", TopUsed_data$model, fixed = TRUE)

#So what are there ratings and reviews and price. 


#Edmonds API key  d2d4xfrkywhw6dmmh55qjuma


#Create a function that gives consumer data ratings for cars pulling from Edmonds

cars <- function(id,make,model,year) {
  
  library(RJSONIO)
  library(RCurl)
  
  #Main part of api
  api_first<- paste("https://api.edmunds.com/api/vehiclereviews/v2/",sep="")
  
  makeLow <-tolower(make)
  modelLow <-tolower(model)
  yearLow <-tolower(year)
  make_mod_yr <- paste(makeLow,modelLow,yearLow,sep = "/")
  
  
  api_last <- paste("?fmt=json&api_key=akw86gbvscxm4szkb3t53rnw",sep="")
  url <- paste(api_first,make_mod_yr,api_last,sep = "")
  addr <- getURL(url)
  
  
  
  
  #JSON parsed
  url.json <- fromJSON(addr)
  
  #Used to count for correct parsing
  # str(url.json,2)
  
  Ratings <- unlist(url.json$averageRating[1])
  
  
  #This gives us all personal weather stations data in area specified by lat and lon
  df_n_ = data.frame(id, makeLow, modelLow, yearLow, Ratings )
  #This returns url, location and station data for lat lon
  return(df_n_)
  
  
}


#NEW top 5 purchased


cars(id=1,make="HONDA",model= "acCord", year = 2015) 
cars(id=2,make="honDa",model= "Cr-v", year = 2014) 
cars(id=3,make="honda",model= "civic", year = 2015) 
cars(id=4,make="honda",model= "odyssey", year = 2015) 
cars(id=5,make="Subaru",model= "forester", year = 2015) 


#Used top 5 purchased



cars(id=1,make="honda",model= "accord", year = 2015) 
cars(id=2,make="honda",model= "Cr-v", year = 2014) 
cars(id=3,make="honda",model= "civic", year = 2015) 
cars(id=4,make="bmw",model= "3-series", year = 2015) 
cars(id=5,make="toyota",model= "camry", year = 2015) 






#This is nice but I want to just add this rating to my data sent of all makes and models

carsdf <- function(df) {
  
  df_ <- df
  # df<-New_data
  
  #Main part of api
  df$api_first<- paste("https://api.edmunds.com/api/vehiclereviews/v2/",sep="")
  
  df$makeLow <-tolower(df$make)
  df$modelLow <-tolower(df$model)
  df$yearLow <-tolower(df$year)
  
  df$make_mod_yr <- paste(df$makeLow,df$modelLow,df$yearLow,sep = "/") 
  
  df$api_last <- paste("?fmt=json&api_key=akw86gbvscxm4szkb3t53rnw",sep="")
  df$url <- paste(df$api_first,df$make_mod_yr,df$api_last,sep = "")
  #     df$urladd <- paste(url[ii],sep = "")
  
  url<-df$url
  
  
  
  
  
  
  masterlist <- list() # Blank master list
  jj = 1 # Counter for incrementing the masterlist
  
  for (ii in 1:length(url)) { 
    #JSON parsed
    
    addr <- getURL(url[ii])    
    
    url.json <- fromJSON(addr)
    
    #Used to count for correct parsing
    #str(url.json,2)
    
    # df$Ratings <- unlist(url.json$averageRating[1])
    
    
    Ratings <- unlist(url.json$averageRating[1])
    # vehic <- unlist(url.json$links$rel)
    
    masterlist[[jj]] <- data.frame(Ratings)
    jj = jj + 1
  } 
  
  car_rating <-  do.call(rbind,masterlist) %>% mutate(id = as.character(rownames(df_),levels=rownames(df_)))
  
  car_rating_ <-df_ %>% inner_join(car_rating)
  
  
  return(car_rating_)
}


carsdf(TopNew_data) -> N1

carsdf(TopUsed_data) -> U1

```


Answer
```{r}


#NEW top 5 purchased


cars(id=1,make="HONDA",model= "acCord", year = 2015) 
cars(id=2,make="honDa",model= "Cr-v", year = 2014) 
cars(id=3,make="honda",model= "civic", year = 2015) 
cars(id=4,make="honda",model= "odyssey", year = 2015) 
cars(id=5,make="Subaru",model= "forester", year = 2015) 


#Used top 5 purchased



cars(id=1,make="honda",model= "accord", year = 2015) 
cars(id=2,make="honda",model= "Cr-v", year = 2014) 
cars(id=3,make="honda",model= "civic", year = 2015) 
cars(id=4,make="bmw",model= "3-series", year = 2015) 
cars(id=5,make="toyota",model= "camry", year = 2015) 


#This is nice but I want to just add this rating to my dataset with of all makes and models

#Below is that information

N1
U1



```